\section{Test Setup}
\label{section: experiments - test setup}
The testing setup will be discussed in detail here, allowing anyone to reproduce the experiments at a later date.
The specific physical setup, including mounting locations, hardware specifications, and environment, will be discussed.
The digital setup will be specified, including all tools used during the testing.
Lastly, the testing procedure, the "script" - so to say - which was followed by the researcher, will be discussed.
% [[ !!!!!!!!! ]]
% Important setup info: FMCW was mounted at 125cm with a very slight upwards tilt (a few degrees)
% The Kinect was located 50cm \textbf{above} the FMCW, and 13cm \textbf{behind} the FMCW at a downward angle.
% [[ !!!!!!!!! ]]


% The experiments took place in a large, open, and empty room.
% The users were briefly informed of what the system was and how they could control it via the pamphlet shown in \cref{appendix: user explanation}.

% Here, I want to discuss the test setup I'm using, the precise location and placement of the various things, as well as my reasoning for that.
% I also want to discuss the different things I've prepared (such as the standardized movement set and the pamphlet \ref{appendix: user explanation}.

\subsection{Physical Setup}
\label{sub-section: experiments - test setup - physical space}
The experiments took place in a large (7 meters wide, 10 meters deep) and open room. 
At times, there was one other person in the room, next to the researcher and the user, this person did not make any macro movements and sat at the edge of the MMWave radar's vision, and was well separated from the user, and should thus have had no significant result on the data collection.
The users were asked to stand at a distance of 2 meters from the FMCW while they used the system and were facing the sensors directly.

The MilliMeter Wave Radar, which was used, was a Texas Instruments IWR6843ISK, and used the \textit{Mobile Tracking} (which can be found in the TI Resource Explorer under \texttt{mmWave radar sensors/Embedded Software/Radar Toolbox/Example Project/Industrial and Personal Electronics/Robotics/Mobile Tracking}).
\textbf{reference potential limitations of this firmware, and refer to the limitations section}

Also show some photos of the setup

% Here I'll show some photos of the physical test setup. Mention the position of all sensors, their specific numbers, accompanied by photos of the room.

\subsection{Digital Setup}
\label{sub-section: experiments - test setup - digital space}
Here I'll discuss the exact software I'm using, mentioning the specific branch on my github, mentioning the way to get the kinect code running, etc, etc.
Mostly so that people can recreate the research if they want to.

\subsection{Testing Procedures}
\label{sub-section: experiments - test setup - testing procedures} 
I'll discuss the way I tested with users. 
I will mention the standardized moveset \ref{appendix: standardized movement set} and will mention the free play section.
I will also mention the types of tips I gave the users between standard sessions (and refer to an appendix which has all that written out in detail).


