\chapter{Experiment Notes}
\label{appendix: experiment notes}

During the experiment, I took some notes on how different people performed good or poorly (in my subjective view).

% Double separation line and spacing
\vspace{2em}
\hrule
\vspace{0.2em}
\hrule

General
Its interesting to look at how experience effects the accuracy of my system AND of Mars DL system, and to see if one might be better with more experienced users.

IDEA: more lenient noise filtering might bring better results with general users, as their arm pointcloud might not be present in as many frames as with more experienced users. 
e.g. Considering 5 frames as opposed to 3 frames in the temporal filtering may increase performance on general users.

The chip seemed to be mounted not perfectly level, with the left part (from the users viewpoint) being ever so slightly too high

User 61
The fact that user 61 had never used the system was quite visible. 
The system has a decent bit of nuance which should be known for effective use, and was not known by the user.
We did 3 standard runs, during the first they barely wove their hands, after that I reminded them that the system works best when you wave your hands, then they moved them up and down quickly (5-10 Hz) or to and from the camera, but with large movements (1-3 Hz).
The third standard run I specified that small movements back and forth towards the camera are best, which resulted in jazz hands.

In the free play sections they experimented with still arms and arms moving to and from. However it seemed like the configuration has their body put a bit too high, as they had difficulty hitting the high notes.

User 94
User 94 had a decent understanding of the system from the get go, but between standard run 1, 2, 3 I still gave them some small tips on how to better use the system.

In standard 2 they moved the wrong arm on a few occasions.


They where also enthusiastic to try the free play section of the experiment.
User 41
In the first standard run they didn’t move their arms a lot, between run 1 and 2 I informed them of the effective methods of moving your arms (for higher data collection), they tried following it, but did not do so consistently.
Between set 2 and 3 I informed them how to have their arms “good”in the zones (as “low”is less low then most think).


User 7
Had some difficulty with the movements.


User 51
They often held their low positions very low, and their high positions very high, which caused some accidental incorrect triggers.

I gave the the advice of moving their hands more (jazz hands) after the first trial, and told them that low wasn’t quite as low as they put it (though they didn’t improve significantly).

In general they had fun and where enthusiastic, but didn’t move their hands a lot, or if they moved they moved their whole arm, and they held high “very high”and low “very low“

User 52
after the first trial I told them about the zone locations and waving, I once again reminded them about that after the second trial, they did try to wave their hands well.
One thing was that it felt like they might’ve been a bit too tall for how I had the system setup, as the center of the MEB seemed to be nearer their chin then their sternum.
