\chapter{Introduction}
\label{chapter: introduction}


The landscape of Human Computer Interactions (HCI) is shifting as our computers are becoming more powerful and more integrated.
Many new electronic devices are not standalone tools anymore, such as the home computer, these devices are now a part of a broader IoT environment, ranging from smart lights to voice assistants.
Controlling this IoT environment with traditional input methods, such as a mouse, keyboard, or touchscreen, is intrusive and impractical.
Modern alternative input methods are needed for these systems.
Smartphone apps and voice-controlled systems do fill this role,  in the form of smartphone apps and voice commands, but a broader set of options is needed.
This thesis proposes such an interface, which perceives the user's pose through a Millimeter Wave (mmWave) radar, and uses that data to control a computer system.
Similar systems have been built before, using the same sensor technology, but these previous systems relied on deep learning models, which are prone to overfitting, may need extensive retraining in new environments, and require an impractical amount of training data to produce good results.
This thesis sets out to design a Human Pose Estimation (HPE) system, using an mmWave sensor, which relies solely on explainable, debuggable, and tunable algorithms.

\input{sections/1. introduction/1.1. motivation}

\input{sections/1. introduction/1.2. research challenge}

\input{sections/1. introduction/1.3. contibutions}

% \input{sections/1. introduction/1.3. scientific gap}
% \input{sections/1. introduction/1.1. background}

% \input{sections/1. introduction/1.2. scientific gap}

% \input{sections/1. introduction/1.3. objective}

% \input{sections/1. introduction/1.4. significance of the research}

% \input{sections/1. introduction/1.5. upcomming chapters}
